Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-19 docs/manuscript/manuscript.tex
Table 3. Summary of optimal clustering index values (Different Clustering Methods)

Next, we compared the best indices values for different algorithm solving methodology to determine the best cuts to confirm that Ward.D2 is the best methodology. Once again, we determined that Ward.D2 was the best algorithm and learned that best cut is four trees by doing analysis within the different indices values of different algorithm theories. We compared the values by choosing KL, Ratkowsky, and Marriot values to compare what is the best cut for different clustering methods.

\begin{table}[h!]
  \centering
  \begin{tabular}{c c m{7cm}}\toprule
    \bf Variable & \bf Description & \bf Definition \\\midrule
    \texttt{imws} 
 & \\\bottomrule
  \end{tabular}
  \caption{Summary of explanatory variables (national averages at household level)}
  \label{tab:summary}
\end{table}

>>>>

Next, we compared the best indices values for different algorithm solving methodology to determine the best cuts to confirm that Ward.D2 is the best methodology. Once again, we determined that Ward.D2 was the best algorithm and learned that the best cut is four trees by analyzing within the different indices values of different algorithm theories. We compared the values by choosing KL, Ratkowsky, and Marriot values to compare what is the best cut for different clustering methods.

\begin{table}[h!]
  \centering
  \begin{tabular}{c c c}\toprule
    \bf Methods & \bf KL (clusters) & \bf Value Index \\\midrule
    \texttt{Ward.D2} & 4 & 2.4982 \\\hline
    \texttt{Ward.D} & 4 & 3.3397 \\\hline
    \texttt{Complete} & 4 & 3.9093 \\\hline
     \texttt{K-Means} & 12 & 8.6836  \\\bottomrule
  \end{tabular}
   \centering
  \begin{tabular}{c c c}\toprule
    \bf Methods & \bf Ratkowsky (clusters) & \bf Value Index \\\midrule
    \texttt{Ward.D2} & 4 & 0.2981 \\\hline
    \texttt{Ward.D} & 4 & 0.2981 \\\hline
    \texttt{Complete} & 3 & 0.3193 \\\hline
     \texttt{K-Means} & 3 & 0.2948 \\\bottomrule
  \end{tabular}
   \centering
  \begin{tabular}{c c c c c}\toprule
    \bf Methods & \bf Marriot(clusters) & \bf Value Index & \bf Gap & \bf Majority Rule  \\\midrule
    \texttt{Ward.D2} & 4 & 1.54E+40 &  8 & 4 \\\hline
    \texttt{Ward.D} & 4 & 1.79E+40 & 8 & 4 \\\hline
    \texttt{Complete} & 4 & 1.77E+40  & 7 & 4 \\\hline
     \texttt{K-Means} & 4 & 1.54E+40  & \texttt{N/A} & 3  \\\bottomrule
  \end{tabular}
  \caption{Summary of optimal clustering index values (Different Clustering Methods)}
  \label{tab:summary}
\end{table}
